Depth and thickness of tectonic tremor in the northeastern Olympic Peninsula

### 2021-11-25 paper/answer_reviewers.tex

\bigskip

\textit{My main comment concerns the bias in the observation of S minus P times. The authors measure the observed lag time from the centroid of the cross-correlation function within the time window 2 seconds before and after the theoretical lag time if the tremor source was on the plate boundary (L330-335). I understand that such kind of constraint is sometimes useful for obtaining realistic solutions, but I am worried whether this constraint works for too strong bias that concentrates all tremor depths to the plate boundary depths. In other words, the S minus P time measurements should be free from theoretical time lags when discussing the spatial relationship between tremor and plate boundary. How about using the whole time window or focusing on the window around the maximum peak? In any case, the authors should check and show that these time window limitations do not strongly affect the results.}

\bigskip

You bring up a very important point regarding the potential of bias in our results and we have explored this in some detail.  We have rewritten our method to include an important detail that we left out of the text of the submitted version which we now explain on lines 264-278.  We have also sent figures to show more clearly the windows we analyze for the clustering relative to the theoretical time and our final observation.  The highest peak in the absolute value of the phase-weighted stacks of the cross correlation functions $S_i (\tau)$ within the defined window is the same as the highest peak between 3 and  8 seconds for every array / tremor grid  except for one (BH 5, -5) so using the theoretical S-P time as a guide to define the time window has very little or no effect on the final travel-time observation.

@@

\bigskip

\textit{L346-358: half width is a typical measure for uncertainties when picking a peak value. In this case, when picking a centroid value, it is more natural to use standard deviation or MAD (or Qn?).}

\bigskip

These are often heavy tailed distributions so the standard deviation, MAD and Qn depend on a choice of the width of the time interval to consider. The half width was chosen because it is independent of a selected width to consider.

@@

\bigskip

\textbf{Additional figures related to first comment from Reviewer 1}

\bigskip

\begin{figure}
\includegraphics[width=\linewidth]{figures/intervals/BS_-05_-05_stacks.eps}
\caption{Stack of the cross-correlation functions for the Big Skidder array for the 110 one-minute long time windows when tremor was detected in a 5 km by 5 km grid cell located 7 kilometers southwest of the array. Red line corresponds to the cross-correlation of the East-West component with the vertical component, and blue line corresponds to the cross-correlation of the North-South component with the vertical component. The solid black line corresponds to the final observed S-P time, the black dotted line is the theoretical S-P time if the source is on the plate boundary, and the grey dashed lines are the intervals $\left[T_{min} ; T_{max}\right]$ where we look for a secondary peak. For all the remaining figures, the two letters abbreviation in the title corresponds to the name of the array, and the numbers in parenthesis indicate the distance from the array to the grid cell in the east direction and the north direction.}
\end{figure}

### 2021-11-25 paper/agujournaltemplate.tex
last version. ready to submit

For each array, and every 5 km by 5 km grid cell located within 25 km, we analyze the one-minute-long time windows corresponding to all the tremor epicenters located within the grid cell. For each three-component seismic station and each channel, we detrended the data, tapered the first and last 5 seconds with a Hann window, removed the instrument response, bandpass filtered between 2 and 8 Hz, and resampled the data to 20 Hz. All these preprocessing operations were done with the Python package obspy. For each seismic station and each one-minute-long time window, we cross correlated the vertical component with the East-West component and with the North-South component. Then, we stacked the cross correlation functions over all the seismic stations of the array. We call this stack $S_{i j} (\tau)$ for time lag $\tau$, the $i$-th channel ($i$=1 or 2 for the North or East channel) and the $j$-th one-minute-long time window for a given epicenter grid/array pair. At each step of this method we experimented with a linear stack, a $n$th-root stack, and a phase-weighted stack ~\cite{SCH_1997} and found that the phase-weighted stack worked best. So, all the stacks discussed here used the phase-weighted method.  Figure 2 shows an example of the envelopes of $S_{i j} (\tau)$ for the Big Skidder array for the 110 one-minute-long time windows when tremor was detected in the 5 km by 5 km grid cell located 7 kilometers southwest of the array. For all time windows, there is a primary peak in the envelopes of the cross-correlation $S_{i j} (\tau)$ at $\tau = 0 s$ (not shown in the Figure). Additionally, for about 40\% of the time windows, we also see a secondary peak in the envelopes of the cross-correlation $S_{i j} (\tau)$ at about $\tau = 4.5 s$. As the energy of the P-waves is expected to be higher on the vertical component, and the energy of the S-waves to be higher on the horizontal components, we interpret this peak to correspond to the time lag between the arrival of the direct P- and S-waves. \\

@@

To improve the signal-to-noise ratio of the peak in the stacked cross-correlation, we divided the one-minute-long time windows into two clusters, the ones that match the stacked cross-correlations well, and the ones that do not. In order to do the clustering, we stacked the stacked cross-correlation functions, $S_{i j} (\tau)$, over all the one-minute-long time windows to obtain $S_i (\tau)$. For each one-minute time window $j$ we cross-correlated $S_i (\tau)$ with $S_{i j} (\tau)$ to obtain $S^c_{i j} (\tau)$. We only want to verify whether the waveform $S_{i j} (\tau)$ around the secondary peak matches well with the stack $S_i (\tau)$. We thus look for the maximum of the absolute value of the stack $S_i (\tau)$ between one second before and one second after the theoretical time lag between P- and S-wave arrival if the source was on the plate boundary. We call the time lag corresponding to this maximum $\tau_{max}$. Then for the cross-correlation between $S_{i j} (\tau)$ and $S_i (\tau)$, we keep only the values of lag times $\tau$ between one second before and one second after $\tau_{max}$. For each $i$ and $j$ we determine 3 numbers from $S^c_{i j} (\tau)$: its value at zero lag time, its maximum absolute value and the time lag at which it takes its maximum absolute value, and we determine one number from $S_{i j} (\tau)$: the ratio of its maximum absolute value $S_{i j} (\tau_{max})$ to its rms. We considered lag times $\tau$ from 12 to 14 seconds to compute the value of the rms of the $S_{i j} (\tau)$. Each one-minute-long time window is thus associated with eight values of quality criteria, four for each of the the East and North channels. We then classified each one-minute-long time window into two different clusters, based on the value of these criteria, using a K-means clustering algorithm (function sklearn.cluster.KMeans from the Python library SciKitLearn). The K-means procedure is as follows: We choose to have 2 clusters, then we arbitrarily choose a center for each cluster. We put each one-minute-long time window into the cluster to which it is closest (based on the values of the eight criteria). Once all one-minute-long time windows have been put in a cluster, we recompute the mean of the eight criteria for each cluster, and iterate the procedure until convergence. On average, about 35\% of the time windows fit well with the stack and are kept in the first cluster, while 65\% do not fit well with the stack and are removed. For each cluster, we then stacked the envelopes of the cross-correlation functions over all the one-minute-long time windows belonging to that cluster using a phase-weighted stack. We tried using more than 2 clusters, but it did not improve the final stack of the best cluster. Figure 3 shows the stack of the envelopes of the $S_{i j} (\tau)$ over the time windows $j$ that correspond to cluster 0 (red) and cluster 1 (blue).  The clustering has greatly improved the amplitude of the peak for cluster 1, and made the peak nearly disappear for cluster 0. \\

@@

We did this analysis for grid cells located in a 50 km by 50 km area centered on each of the eight arrays. We thus consider up to 11 * 11 * 8 = 968 values of the time lag between the direct P-wave and S-wave. We assumed that the epicenter is at the center of the grid and determined the depth that satisfies that epicenter and the observed S-minus-P time. The velocity models are taken from the 3D velocity model from ~\citeA{MER_2020}. For each array, we looked for the closest grid point (in terms of latitude and longitude) in the 3D model by ~\citeA{MER_2020} and used the corresponding layered model of compressional and shear wave speeds to compute the tremor depth. We thus used 8 different 1D velocity models corresponding to the 8 arrays. This allows us to take into account the substantial variations of the Poisson's ratio in the East-West direction.

@@

To compute the depth, we select the EW or the NS component with the larger maximum value of the peak. We focus on the part of the stack of the envelopes of the cross-correlation functions located between 2 seconds before and 2 seconds after the time lag $\tau_{max}$ corresponding to the secondary peak obtained earlier. We computed the moment centroid of this part of the stack and assumed that it was equal to the time lag between the arrivals of the direct P-wave and the direct S-wave. We then computed the corresponding depth of the source of the tremor for all the locations of the source of the tremor.To verify the effect of the width of the time window for which we compute the moment centroid, we compute the centroid and the corresponding depth of the source for widths equal to 2 seconds, 4 seconds, and 6 seconds. We compute the variations in depths when decreasing the width from 4 seconds to 2 seconds. 87\% of the differences in depth are under 2 kilometers. The median difference is 0.064 km, so there is no bias towards shallower or deeper depths when we decrease the width of the time window. When we compute the variations in depths when increasing the width from 4 seconds to 6 seconds, 84\% of the differences in depth are under 2 kilometers and the median difference is 0.054 km. We did the same analysis for the eight arrays of the experiment and each of the tremor-location grid points. The corresponding stacks of the envelopes are shown in Figures S1 to S7 in the supplementary material. For the two arrays Cat Lake and Lost Cause, there are very few source-array locations that have both enough tremor and a high ratio between the peak and the root mean square. Moreover, for the locations where we have a peak, the peak is often not very clear and stretched along the time axis. We did not use data from these two arrays. For the Port Angeles array, there is only a clear peak for a near vertical incidence of the seismic waves. We choose to keep this array in the analysis in order to have two additional data points in the westernmost region of the study area. \\

>>>>

For each array, and every 5 km by 5 km grid cell located within 25 km, we analyze the one-minute-long time windows corresponding to all the tremor epicenters located within the grid cell. For each three-component seismic station and each channel, we detrended the data, tapered the first and last 5 seconds with a Hann window, removed the instrument response, bandpass filtered between 2 and 8 Hz, and resampled the data to 20 Hz. All these preprocessing operations were done with the Python package obspy. For each seismic station and each one-minute-long time window, we cross correlated the vertical component with the East-West component and with the North-South component. Then, we stacked the cross correlation functions over all the seismic stations of the array. We call this stack $S_{i j} (\tau)$ for time lag $\tau$, the $i$-th channel ($i$=1 or 2 for the North or East channel) and the $j$-th one-minute-long time window for a given epicenter grid/array pair. At each step of this method we experimented with a linear stack, a $n$th-root stack, and a phase-weighted stack ~\cite{SCH_1997} and found that the phase-weighted stack worked best. So, all the stacks discussed here used the phase-weighted method.  Figure 2 shows an example of the envelopes of $S_{i j} (\tau)$ for the Big Skidder array for the 110 one-minute-long time windows when tremor was detected in the 5 km by 5 km grid cell located 7 kilometers southwest of the array. For all time windows, there is a peak in the envelopes of the cross-correlation $S_{i j} (\tau)$ at $\tau = 0 s$ (not shown in the figure). Additionally, for about 40\% of the time windows, we also see another peak in the envelopes of the cross-correlation $S_{i j} (\tau)$ at about $\tau = 4.5 s$. As the energy of the P-waves is expected to be higher on the vertical component, and the energy of the S-waves to be higher on the horizontal components, we interpret this peak to correspond to the time lag between the arrival of the direct P- and S-waves. This peak is only seen for the positive time lag, and no peak is seen in the negative part of the cross-correlation. \\

@@

To determine which time window to use for further consideration we compute the theoretical value of the time lag between the P- and S-wave arrivals if the source was located on the plate boundary. We then look for the lag time corresponding to the peak of the absolute value of the stack within 1 second of the theoretical lag time. We do this nine times for each combination of 3 stacking methods acting on the stack of stations for each array and on the stacks across each of the one-minute time windows. The stacking methods are a linear stack, a $n$th-root stack or a phase-weighted stack. We define $T_{min}$ to be the minimum of these 9 lag times minus 1 s and $T_{max}$ to be the maximum of these 9 times plus 1 s. We limit the rest of our analysis to the time window $\left[ T_{min} ; T_{max} \right]$. We define $\tau_{max}$ to be the time corresponding to the peak absolute value of the phase-weighted stack within these time limits. $\tau_{max}$ turns out to also be the time corresponding to the maximum of the stacked correlations within a fixed wide window from 3-8 s for all the array / grid pairs except for one (BH, grid that is 7 km to the southeast). This suggests that there is very little, if any, bias in our method forcing our final observed S minus P times towards their theoretical values. \\

To improve the signal-to-noise ratio of the peak in the stacked cross-correlation, we divided the one-minute-long time windows into two clusters, the ones that match the stacked cross-correlations well, and the ones that do not. In order to do the clustering, we stacked the stacked cross-correlation functions, $S_{i j} (\tau)$, over all the one-minute-long time windows to obtain $S_i (\tau)$. For each one-minute time window $j$ we cross-correlated $S_i (\tau)$ with $S_{i j} (\tau)$ to obtain $S^c_{i j} (\tau)$. We want to verify whether the waveform $S_{i j} (\tau)$ around the peak $\tau_{max}$ matches well with the stack $S_i (\tau)$. For the cross-correlation between $S_{i j} (\tau)$ and $S_i (\tau)$, we keep only the values of lag times $\tau$ between $T_{min}$ and $T_{max}$. For each $i$ and $j$ we determine 3 numbers from $S^c_{i j} (\tau)$: its value at zero lag time, its maximum absolute value and the time lag at which it takes its maximum absolute value, and we determine one number from $S_{i j} (\tau)$: the ratio of its maximum absolute value $S_{i j} (\tau) _{max}$ to its rms. We considered lag times $\tau$ from 12 to 14 seconds to compute the value of the rms of the $S_{i j} (\tau)$. Each one-minute-long time window is thus associated with eight values of quality criteria, four for each of the the East and North channels. We then classified each one-minute-long time window into two different clusters, based on the value of these criteria, using a K-means clustering algorithm (function sklearn.cluster.KMeans from the Python library SciKitLearn). The K-means procedure is as follows: We choose to have 2 clusters, then we arbitrarily choose a center for each cluster. We put each one-minute-long time window into the cluster to which it is closest (based on the values of the eight criteria). Once all one-minute-long time windows have been put in a cluster, we recompute the mean of the eight criteria for each cluster, and iterate the procedure until convergence. On average, about 35\% of the time windows fit well with the stack and are kept in the first cluster, while 65\% do not fit well with the stack and are removed. For each cluster, we then stacked the envelopes of the cross-correlation functions over all the one-minute-long time windows belonging to that cluster using a phase-weighted stack. We tried using more than 2 clusters, but it did not improve the final stack of the best cluster. Figure 3 shows the stack of the envelopes of the $S_{i j} (\tau)$ over the time windows $j$ that correspond to cluster 0 (red) and cluster 1 (blue).  The clustering has greatly improved the amplitude of the peak for cluster 1, and made the peak nearly disappear for cluster 0. \\

@@

We did this analysis for grid cells located in a 50 km by 50 km area centered on each of the eight arrays. We thus consider up to 11 * 11 * 8 = 968 values of the time lag between the direct P-wave and S-wave. We assumed that the epicenter is at the center of the grid and determined the depth that satisfies that epicenter and the observed S-minus-P time. The velocity models are taken from the 3D velocity model from ~\citeA{MER_2020}. For each array, we looked for the closest grid point (in terms of latitude and longitude) in the 3D model by ~\citeA{MER_2020} and used the corresponding layered model of compressional and shear wave speeds to compute the tremor depth. We thus used 8 different 1D velocity models corresponding to the 8 arrays. This allows us to take into account the substantial variations of the Poisson's ratio in the East-West direction. \\

@@

To compute the depth, we select the EW or the NS component with the larger maximum value of the peak. We focus on the part of the stack of the envelopes of the cross-correlation functions located between 2 seconds before and 2 seconds after the time lag $\tau_{max}$ corresponding to the peak obtained earlier. We computed the moment centroid of this part of the stack and assumed that it was equal to the time lag between the arrivals of the direct P-wave and the direct S-wave. We then computed the corresponding depth of the source of the tremor for all the locations of the source of the tremor. To verify the effect of the width of the time window for which we compute the moment centroid, we compute the centroid and the corresponding depth of the source for widths equal to 2 seconds, 4 seconds, and 6 seconds. We compute the variations in depths when decreasing the width from 4 seconds to 2 seconds. 87\% of the differences in depth are under 2 kilometers. The median difference is 0.064 km, so there is no bias towards shallower or deeper depths when we decrease the width of the time window. When we compute the variations in depths when increasing the width from 4 seconds to 6 seconds, 84\% of the differences in depth are under 2 kilometers and the median difference is 0.054 km. The corresponding stacks of the envelopes are shown in Figure 4 and Figures S1 to S7 in the supplementary material. For the two arrays Cat Lake and Lost Cause, there are very few source-array locations that have both enough tremor and a high ratio between the peak and the root mean square. Moreover, for the locations where we have a peak, the peak is often not very clear and stretched along the time axis. We did not use data from these two arrays. For the Port Angeles array, there is only a clear peak for a near vertical incidence of the seismic waves. We choose to keep this array in the analysis in order to have two additional data points in the westernmost region of the study area. \\

### 2021-11-25 paper/agujournaltemplate_highlighted.tex
last version. ready to submit

For each array, and every 5 km by 5 km grid cell located within 25 km, we analyze the one-minute-long time windows corresponding to all the tremor epicenters located within the grid cell. For each three-component seismic station and each channel, we detrended the data, tapered the first and last 5 seconds with a Hann window, removed the instrument response, bandpass filtered between 2 and 8 Hz, and resampled the data to 20 Hz. All these preprocessing operations were done with the Python package obspy. For each seismic station and each one-minute-long time window, we cross correlated the vertical component with the East-West component and with the North-South component. Then, we stacked the cross correlation functions over all the seismic stations of the array. We call this stack $S_{i j} (\tau)$ for time lag $\tau$, the $i$-th channel ($i$=1 or 2 for the North or East channel) and the $j$-th one-minute-long time window for a given epicenter grid/array pair. At each step of this method we experimented with a linear stack, a $n$th-root stack, and a phase-weighted stack ~\cite{SCH_1997} and found that the phase-weighted stack worked best. So, all the stacks discussed here used the phase-weighted method.  Figure 2 shows an example of the envelopes of $S_{i j} (\tau)$ for the Big Skidder array for the 110 one-minute-long time windows when tremor was detected in the 5 km by 5 km grid cell located 7 kilometers southwest of the array. \textbf{For all time windows, there is a primary peak in the envelopes of the cross-correlation $S_{i j} (\tau)$ at $\tau = 0 s$ (not shown in the Figure). Additionally, for about 40\% of the time windows, we also see a secondary peak in the envelopes of the cross-correlation $S_{i j} (\tau)$ at about $\tau = 4.5 s$.} As the energy of the P-waves is expected to be higher on the vertical component, and the energy of the S-waves to be higher on the horizontal components, we interpret this peak to correspond to the time lag between the arrival of the direct P- and S-waves. \\

@@

To improve the signal-to-noise ratio of the peak in the stacked cross-correlation, we divided the one-minute-long time windows into two clusters, the ones that match the stacked cross-correlations well, and the ones that do not. In order to do the clustering, we stacked the stacked cross-correlation functions, $S_{i j} (\tau)$, over all the one-minute-long time windows to obtain $S_i (\tau)$. For each one-minute time window $j$ we cross-correlated $S_i (\tau)$ with $S_{i j} (\tau)$ to obtain $S^c_{i j} (\tau)$. \textbf{We only want to verify whether the waveform $S_{i j} (\tau)$ around the secondary peak matches well with the stack $S_i (\tau)$. We thus look for the maximum of the absolute value of the stack $S_i (\tau)$ between one second before and one second after the theoretical time lag between P- and S-wave arrival if the source was on the plate boundary. We call the time lag corresponding to this maximum $\tau_{max}$. Then for the cross-correlation between $S_{i j} (\tau)$ and $S_i (\tau)$}, we keep only the values of lag times $\tau$ between one second before and one second after \textbf{$\tau_{max}$}. For each $i$ and $j$ we determine 3 numbers from $S^c_{i j} (\tau)$: its value at zero lag time, its maximum absolute value and the time lag at which it takes its maximum absolute value, and we determine one number from $S_{i j} (\tau)$: the ratio of its maximum absolute value \textbf{$S_{i j} (\tau_{max})$} to its rms. We considered lag times $\tau$ from 12 to 14 seconds to compute the value of the rms of the $S_{i j} (\tau)$. Each one-minute-long time window is thus associated with eight values of quality criteria, four for each of the the East and North channels. We then classified each one-minute-long time window into two different clusters, based on the value of these criteria, using a K-means clustering algorithm (function sklearn.cluster.KMeans from the Python library SciKitLearn). The K-means procedure is as follows: We choose to have 2 clusters, then we arbitrarily choose a center for each cluster. We put each one-minute-long time window into the cluster to which it is closest (based on the values of the eight criteria). Once all one-minute-long time windows have been put in a cluster, we recompute the mean of the eight criteria for each cluster, and iterate the procedure until convergence. On average, about 35\% of the time windows fit well with the stack and are kept in the first cluster, while 65\% do not fit well with the stack and are removed. For each cluster, we then stacked the envelopes of the cross-correlation functions over all the one-minute-long time windows belonging to that cluster using a phase-weighted stack. We tried using more than 2 clusters, but it did not improve the final stack of the best cluster. Figure 3 shows the stack of the envelopes of the $S_{i j} (\tau)$ over the time windows $j$ that correspond to cluster 0 (red) and cluster 1 (blue).  The clustering has greatly improved the amplitude of the peak for cluster 1, and made the peak nearly disappear for cluster 0. \\

@@

\textbf{To compute the depth, we select the EW or the NS component with the larger maximum value of the peak.} We focus on the part of the stack of the envelopes of the cross-correlation functions located between 2 seconds before and 2 seconds after the \textbf{time lag $\tau_{max}$ corresponding to the secondary peak obtained earlier}. We computed the moment centroid of this part of the stack and assumed that it was equal to the time lag between the arrivals of the direct P-wave and the direct S-wave. We then computed the corresponding depth of the source of the tremor for all the locations of the source of the tremor. \textbf{To verify the effect of the width of the time window for which we compute the moment centroid, we compute the centroid and the corresponding depth of the source for widths equal to 2 seconds, 4 seconds, and 6 seconds. We compute the variations in depths when decreasing the width from 4 seconds to 2 seconds. 87\% of the differences in depth are under 2 kilometers. The median difference is 0.064 km, so there is no bias towards shallower or deeper depths when we decrease the width of the time window. When we compute the variations in depths when increasing the width from 4 seconds to 6 seconds, 84\% of the differences in depth are under 2 kilometers and the median difference is 0.054 km.} We did the same analysis for the eight arrays of the experiment \textbf{and each of the tremor-location grid points}. The corresponding stacks of the envelopes are shown in Figures S1 to S7 in the supplementary material. For the two arrays Cat Lake and Lost Cause, there are very few source-array locations that have both enough tremor and a high ratio between the peak and the root mean square. Moreover, for the locations where we have a peak, the peak is often not very clear and stretched along the time axis. We did not use data from these two arrays. For the Port Angeles array, there is only a clear peak for a near vertical incidence of the seismic waves. We choose to keep this array in the analysis in order to have two additional data points in the westernmost region of the study area. \\

>>>>

For each array, and every 5 km by 5 km grid cell located within 25 km, we analyze the one-minute-long time windows corresponding to all the tremor epicenters located within the grid cell. For each three-component seismic station and each channel, we detrended the data, tapered the first and last 5 seconds with a Hann window, removed the instrument response, bandpass filtered between 2 and 8 Hz, and resampled the data to 20 Hz. All these preprocessing operations were done with the Python package obspy. For each seismic station and each one-minute-long time window, we cross correlated the vertical component with the East-West component and with the North-South component. Then, we stacked the cross correlation functions over all the seismic stations of the array. We call this stack $S_{i j} (\tau)$ for time lag $\tau$, the $i$-th channel ($i$=1 or 2 for the North or East channel) and the $j$-th one-minute-long time window for a given epicenter grid/array pair. At each step of this method we experimented with a linear stack, a $n$th-root stack, and a phase-weighted stack ~\cite{SCH_1997} and found that the phase-weighted stack worked best. So, all the stacks discussed here used the phase-weighted method.  Figure 2 shows an example of the envelopes of $S_{i j} (\tau)$ for the Big Skidder array for the 110 one-minute-long time windows when tremor was detected in the 5 km by 5 km grid cell located 7 kilometers southwest of the array. \textbf{For all time windows, there is a peak in the envelopes of the cross-correlation $S_{i j} (\tau)$ at $\tau = 0 s$ (not shown in the figure). Additionally, for about 40\% of the time windows, we also see another peak in the envelopes of the cross-correlation $S_{i j} (\tau)$ at about $\tau = 4.5 s$.} As the energy of the P-waves is expected to be higher on the vertical component, and the energy of the S-waves to be higher on the horizontal components, we interpret this peak to correspond to the time lag between the arrival of the direct P- and S-waves. \textbf{This peak is only seen for the positive time lag, and no peak is seen in the negative part of the cross-correlation.} \\

@@

\textbf{To determine which time window to use for further consideration we compute the theoretical value of the time lag between the P- and S-wave arrivals if the source was located on the plate boundary. We then look for the lag time corresponding to the peak of the absolute value of the stack within 1 second of the theoretical lag time. We do this nine times for each combination of 3 stacking methods acting on the stack of stations for each array and on the stacks across each of the one-minute time windows. The stacking methods are a linear stack, a $n$th-root stack or a phase-weighted stack. We define $T_{min}$ to be the minimum of these 9 lag times minus 1 s and $T_{max}$ to be the maximum of these 9 times plus 1 s. We limit the rest of our analysis to the time window $\left[ T_{min} ; T_{max} \right]$. We define $\tau_{max}$ to be the time corresponding to the peak absolute value of the phase-weighted stack within these time limits. $\tau_{max}$ turns out to also be the time corresponding to the maximum of the stacked correlations within a fixed wide window from 3-8 s for all the array / grid pairs except for one (BH, grid that is 7 km to the southeast). This suggests that there is very little, if any, bias in our method forcing our final observed S minus P times towards their theoretical values.} \\

To improve the signal-to-noise ratio of the peak in the stacked cross-correlation, we divided the one-minute-long time windows into two clusters, the ones that match the stacked cross-correlations well, and the ones that do not. In order to do the clustering, we stacked the stacked cross-correlation functions, $S_{i j} (\tau)$, over all the one-minute-long time windows to obtain $S_i (\tau)$. For each one-minute time window $j$ we cross-correlated $S_i (\tau)$ with $S_{i j} (\tau)$ to obtain $S^c_{i j} (\tau)$. \textbf{We want to verify whether the waveform $S_{i j} (\tau)$ around the peak $\tau_{max}$ matches well with the stack $S_i (\tau)$. For the cross-correlation between $S_{i j} (\tau)$ and $S_i (\tau)$, we keep only the values of lag times $\tau$ between $T_{min}$ and $T_{max}$}. For each $i$ and $j$ we determine 3 numbers from $S^c_{i j} (\tau)$: its value at zero lag time, its maximum absolute value and the time lag at which it takes its maximum absolute value, and we determine one number from $S_{i j} (\tau)$: the ratio of its maximum absolute value \textbf{$S_{i j} (\tau) _{max}$} to its rms. We considered lag times $\tau$ from 12 to 14 seconds to compute the value of the rms of the $S_{i j} (\tau)$. Each one-minute-long time window is thus associated with eight values of quality criteria, four for each of the the East and North channels. We then classified each one-minute-long time window into two different clusters, based on the value of these criteria, using a K-means clustering algorithm (function sklearn.cluster.KMeans from the Python library SciKitLearn). The K-means procedure is as follows: We choose to have 2 clusters, then we arbitrarily choose a center for each cluster. We put each one-minute-long time window into the cluster to which it is closest (based on the values of the eight criteria). Once all one-minute-long time windows have been put in a cluster, we recompute the mean of the eight criteria for each cluster, and iterate the procedure until convergence. On average, about 35\% of the time windows fit well with the stack and are kept in the first cluster, while 65\% do not fit well with the stack and are removed. For each cluster, we then stacked the envelopes of the cross-correlation functions over all the one-minute-long time windows belonging to that cluster using a phase-weighted stack. We tried using more than 2 clusters, but it did not improve the final stack of the best cluster. Figure 3 shows the stack of the envelopes of the $S_{i j} (\tau)$ over the time windows $j$ that correspond to cluster 0 (red) and cluster 1 (blue).  The clustering has greatly improved the amplitude of the peak for cluster 1, and made the peak nearly disappear for cluster 0. \\

@@

\textbf{To compute the depth, we select the EW or the NS component with the larger maximum value of the peak.} We focus on the part of the stack of the envelopes of the cross-correlation functions located between 2 seconds before and 2 seconds after the \textbf{time lag $\tau_{max}$ corresponding to the peak obtained earlier}. We computed the moment centroid of this part of the stack and assumed that it was equal to the time lag between the arrivals of the direct P-wave and the direct S-wave. We then computed the corresponding depth of the source of the tremor for all the locations of the source of the tremor. \textbf{To verify the effect of the width of the time window for which we compute the moment centroid, we compute the centroid and the corresponding depth of the source for widths equal to 2 seconds, 4 seconds, and 6 seconds. We compute the variations in depths when decreasing the width from 4 seconds to 2 seconds. 87\% of the differences in depth are under 2 kilometers. The median difference is 0.064 km, so there is no bias towards shallower or deeper depths when we decrease the width of the time window. When we compute the variations in depths when increasing the width from 4 seconds to 6 seconds, 84\% of the differences in depth are under 2 kilometers and the median difference is 0.054 km.} The corresponding stacks of the envelopes are shown in \textbf{Figure 4 and Figures S1 to S7} in the supplementary material. For the two arrays Cat Lake and Lost Cause, there are very few source-array locations that have both enough tremor and a high ratio between the peak and the root mean square. Moreover, for the locations where we have a peak, the peak is often not very clear and stretched along the time axis. We did not use data from these two arrays. For the Port Angeles array, there is only a clear peak for a near vertical incidence of the seismic waves. We choose to keep this array in the analysis in order to have two additional data points in the westernmost region of the study area. \\
